Article title

### 2019-07-12 NAR_DRAFT.tex
check in figure 2
check in figure 1
check in signature words
check in

\subsection{Real tumor data.}
\subsubsection{Acute Myeloid Leukemia}
We downloaded the whole genome sequence for aml31 \bkmcomment{citation and download date} \cite{Griffith2015}.
We merged the gold and platinum lists, and define is \textit{not present} any variant for which deep sequencing was performed and zero alternate reads were observed.
This is a very conservative metric.
\subsubsection{What I call the cell paper} Not sure if this will get used.

\begin{figure}[t]
\begin{center}
\includegraphics{figures/aml_plot.pdf}
\end{center}
\caption{Performance on aml 31.}
\label{NAR-fig1}
\end{figure}

@@

\begin{figure*}[t]
\begin{center}
\includegraphics{figures/fig1.pdf}
\end{center}
\caption{Model performance on 500X simulated whole exome.
\textbf{(a)} Precision recall curves and \textbf{(c)} Reciever operating characteristic curves for 3 mutation signatures.
Distribution of estimated true positive probabilities for true positive (top) and true negative (bottom) variants for \textbf{b)} the MuTect model and \textbf{d)} the Calibrated model.
A perfectly calibrated model would generate the diagonal line.
}
\label{NAR-fig2}
\end{figure*}

>>>>

\subsection{Real tumor data.}
\subsubsection{Acute Myeloid Leukemia}
We downloaded the whole genome sequence for aml31 \bkmcomment{citation and download date} \cite{Griffith2015}.
We merged the gold and platinum lists, and define as \textit{not present} any variant for which deep sequencing was performed and zero alternate reads were observed.
This is a very conservative metric.
\subsubsection{What I call the cell paper} Not sure if this will get used.

\begin{figure}[t]
\begin{center}
\includegraphics{figures/fig1.pdf}
\end{center}
\caption{Signature words.}
\label{NAR-fig1}
\end{figure}

@@

\begin{figure*}[t]
\begin{center}
\includegraphics{figures/fig2.pdf}
\end{center}
\caption{Model performance on 500X simulated whole exome.
\textbf{(a)} Precision recall curves and \textbf{(c)} Reciever operating characteristic curves for 3 mutation signatures.
Distribution of estimated true positive probabilities for true positive (top) and true negative (bottom) variants for \textbf{b)} the MuTect model and \textbf{d)} the Calibrated model.
A perfectly calibrated model would generate the diagonal line.
}
\label{NAR-fig2}
\end{figure*}
